Lens Modeling in \sw

### 2013-12-12 text/tex/results.tex
editing sec3

To estimate the performance of the volunteers and the quality of the generated models, two tests T1 and T2 were done.

The second test T2 was to compare the desired results of a modeling process, the mass distribution of the lens $\kappa(x, y)$.

The \sw sims were generated by AM, in consultation with PM and AV.

>>>>

The \sw sims were generated by AM, in consultation with PM and AV.
To estimate the performance of the volunteers and the quality of the generated models, two analyses  were done.
The first tested the correct identification and ordering of lensed images.
The second compared the mass distribution of the lens $\kappa(x, y)$ of the generated models to the mass distribution of the simulations.
